---
title: "Compound Interest Shiny App"
author: "Tarvela"
date: "5 décembre 2017"
output: ioslides_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(knitr)
library(kableExtra)
```

## Introduction

Compound interest is present in most banking applications used in day to day operations. A good understanding is needed to make most of our savings potential and to make a good retirement planning.

\newline \newline

*“Compound interest is the eighth wonder of the world. He who understands it, earns it ... he who doesn't ... pays it.”*

- Albert Einstein

##The following application will:
- Calculate possible earnings from savings
- Have an idea of loan interests
- Help me pass to the Coursera class "Developping Data Products" :)


## Parameters
The following parameters can be set in the app:

* Annual investment returns
* Investment returns variation
* Annual inflation
* Inflation variation

## Slide with R Output
As an example of compound interest the following lines will simulate a 5 year deposit of 1000$ at 5%
```{r cars, echo = TRUE, warning=FALSE}
x <- NULL
x$Years <- 1:5
x$money <- 1000*(1.05^x$Years)
x
```

## Slide with Plot

```{r ,echo=FALSE}
library(shiny)
shinyApp(
  
  ui = fluidPage(
  # Application title
  titlePanel("Compound Interest Calculator"),
  
  # Parameters 
  sidebarLayout(
    sidebarPanel(
      textInput("initialSum", "Initial Investment", value = 1000000, width = NULL, placeholder = NULL),
       sliderInput("return",
                   "Annual return of Investments (%)",
                   min = -10,
                   max = 20,
                   value = 5),
      sliderInput("returnVar",
                  "Investment returns variation (+/- %)",
                  min = 0,
                  max = 5,
                  value = 1),
       sliderInput("inflation",
                   "Annual inflation (%)",
                   min = -10,
                   max = 10,
                   value = 2),
      sliderInput("inflationVar",
                  "Inflation variation (+/- %)",
                  min = 0,
                  max = 5,
                  value = 0)
    ),
    # Show a plot of the generated distribution
    mainPanel(
      tabsetPanel(
        tabPanel("Plot",plotOutput("distPlot")),
        tabPanel("Documentation", verbatimTextOutput("doc"))
      )
    )
  )
),
server = function(input, output) {
  output$doc <- renderText({ "Compound Interest Calculator
This simple application helps to visualize the possible returns of a sum knowing the return rate, the return rate variation, the inflation and inflation variation.

To use this app the user only has to enter each parameter and visualize the plot.
    " })
  output$distPlot <- renderPlot({
    x<-NULL
    correctedReturn <- ((1+(input$return/100))/(1+(input$inflation/100)))
    x$Years <- 1:20
    test<- as.integer(input$initialSum)
    cat(test+1)
    x$cR <- ((correctedReturn)^(x$Years)*test)
    x$mincR <- ((correctedReturn*(1-(input$returnVar/100))*(1-(input$inflationVar/100)))^(x$Years)*test)
    x$maxcR <- ((correctedReturn*(1+(input$returnVar/100))*(1+(input$inflationVar/100)))^(x$Years)*test)
  
    plot(x= x$Years, y=((x$cR)), type='l',col = 'darkgray',	xlab="Years", ylab="Dollars [$]", main="Compound Interest Graph", ylim=c(min(x$mincR),max(x$maxcR)))
    lines(x$Years, x$mincR, col = 'grey')
    lines(x$Years, x$maxcR, col = 'grey')
    polygon(c(x$Years, rev(x$Years)), c(x$maxcR, rev(x$mincR)),
            col = rgb(0.1,0.5,0.3,0.1), border = NA)
  })
},
options = list(height = 1500)
)

```

